Algomusicology, ????, Profit

### 2016-05-29 paper.tex
Make Gnomes' saying consistent with title.
Fix quotes.

The South Park Underpants Gnomes\cite{Gnomes} are renowned for their business plan:
\begin{enumerate}
    \item Collect underpants
    \item ?
    \item Profit
\end{enumerate}

@@

For the Gayte-Williams-Thicke constant. I wrote a version of 'Blurred Lines' with three parts and used a three part encoding.

@@

Thank you to the StrangeLoop conference of 2015, which accepted the talk 'Kolmogorov Music' from which this paper derives.

>>>>

The South Park Underpants Gnomes\cite{Gnomes} are renowned for their business plan:
\begin{enumerate}
    \item Collect underpants
    \item ????
    \item Profit
\end{enumerate}

@@

For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.

@@

Thank you to the StrangeLoop conference of 2015, which accepted the talk `Kolmogorov Music' from which this paper derives.
